Equipo 7

### 2021-05-08 final/script.Rmd
Update script.Rmd

censo_10_localidad<-censo_10 %>% 
                    select(ClaveEnt,Entidad,              #EN ESTE SELECT AGREGAMOS LAS VARIABLES QUE NECESITEMOS
                           ClaveMun,Municipio,
                           Localidad, ClaveLoc,
                           vph_inter,vivtot,vph_pc) %>% 
                    mutate(internet_10= vph_inter*100/vivtot,
                           pc_10 =vph_pc*100/vivtot)
#OJO: 84,690 MISSING VALUES PROVENIENTES DE LA BASE DE DATOS

>>>>

censo_10_localidad<-censo_10 %>% 
  select(ClaveEnt,Entidad,              #EN ESTE SELECT AGREGAMOS LAS VARIABLES QUE NECESITEMOS
         ClaveMun,Municipio,
         Localidad, ClaveLoc,
         pobtot,vivpar_hab,vph_inter,vivtot,vph_pc,phog_ind,p15ym_se,graproes,pocupada,psinder,tothog,hogjef_f,
         vph_cel,tam_loc) %>% 
  mutate(internet_10= vph_inter*100/vivpar_hab,
         pc_10 =vph_pc*100/vivpar_hab,
         pobindig_10=phog_ind*100/pobtot,
         p15sinesc_10=p15ym_se*100/pobtot,
         promesc_10=graproes*100/pobtot,
         pocup_10=pocupada*100/pobtot,
         psinsalud_10=psinder*100/pobtot,
         jefmujer_10=hogjef_f*100/vivpar_hab,
         cel_10=vph_cel*100/vivpar_hab)

#OJO: 84,690 MISSING VALUES PROVENIENTES DE LA BASE DE DATOS
